### 2012-05-16 docs/matching_algo/matching_algo.tex
Add some TODOs to the matching algorithm notes
Fill in the last correctness proof for matching algorithm
Just need to show completeness now.

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{graphicx}

@@

@@

\section{Testing Wrapper: Concrete Matching Only}
\label{sec:test-wrapper}

@@

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{graphicx}

@@

\newcommand{\TODOitem}{%
\typeout{WARNING!!! there is still a TODO left}
\color{blue}\item
}
\newcommand{\TODO}[1]{%
\typeout{WARNING!!! there is still a TODO left}
\marginpar{\textbf{!TODO: }\emph{#1}}
}
\newcommand{\TODOinline}[1]{%
\typeout{WARNING!!! there is still a TODO left}
{\color{blue}\textbf{!TODO: }#1}
}

@@

\subsubsection{Completeness}

\TODOinline{all possible ways of satisfying the postconditions are found}
\section{Testing Wrapper: Concrete Matching Only}
\label{sec:test-wrapper}

@@

At the end of the algorithm, everything that was ever in the concrete part of the graph except for bare wires has been added to $m$ by the concrete matching step (postcondition \ref{enum:il-postcond-all-matched}, together with the fact that we always add everything concrete and unmatched to $U_w$, $U_c$ and $U_n$, except bare wires).  We have no more $!$-boxes, so the entire graph is concrete.  $P$ is also empty.  We matched bare wires at the last stage, so $m$ is in fact total on $L$.  So, by the argument in section \ref{sec:match-state}, $m$ is a valid match from the final state of $L$ to $G$.  Since we have only ever performed valid $!$-box operations on $L$, this is a valid instance of $L$, and hence we have found a valid matching from $L$ to $G$.

\subsection{Completeness}

\TODOinline{all possible matchings are found}
